### 2019-10-14 paper/introduction.tex
Minor changes before proofreading

Indeed, there are various researches that revolve around starting the
\glspl{MSR} with fissile materials alternative to $^{233}$U. Many of these
researches focus on the fast-spectrum \glspl{MSR} \cite{heuer2014towards,ashraf2019modeling,
	ashraf2018nuclear, rykhlevskii_fuel_2019, betzler_impacts_2019,
	fiorina2013investigation}, while little focus on
thermal-spectrum \glspl{MSR} \cite{betzler2016modeling,
	zou2018transition,zou2018preliminary}. Nevertheless, simulating the operation of the \gls{SD-TMSR} concept with other
fissile materials (except $^{233}$U) was not studied before. Therefore,
the main object of the present paper is to discuss the simulation of the
\gls{SD-TMSR} operation for a lifetime-long period of time (60 years) with
different initial fissile materials and without any external feed of $^{233}$U
to achieve the thorium fuel cycle transition. We investigated five different
initial fissile materials: \gls{LEU}, Pu mixed with \gls{LEU}, Pu reactor-grade, \gls{TRU} from LWR SNF and $^{233}$U \cite{de2000scenarios}. Moreover, two different feed mechanisms were selected:

\begin{itemize}
	\item Thorium feed mechanism: continuous feed flow of thorium from Th stockpile and $^{233}$U from \texttt{Pa-decay tank}\footnote{An imaginary tank used to store protactinium extracted from the core.}, where the removal rate of $^{233}$Pa = feed rate of $^{233}$U. \cite{betzler2016modeling}.
	\item Non-thorium feed mechanism: continuous injection of Heavy Metal (HM) (excluding Th) and simultaneously feed of all or part of produced $^{233}$U from \texttt{Pa-decay tank}.
\end{itemize}

>>>>

Indeed, there are various researches that revolve around starting the
\glspl{MSR} with fissile materials alternative to $^{233}$U. Many of these
researches focus on the fast-spectrum \glspl{MSR} \cite{heuer2014towards,ashraf2019modeling,
	ashraf2018nuclear, rykhlevskii_fuel_2019, betzler_impacts_2019,
	fiorina2013investigation}, while little focus on
thermal-spectrum \glspl{MSR} \cite{betzler2016modeling,
	zou2018transition,zou2018preliminary}. Nevertheless, simulating the operation of the \gls{SD-TMSR} concept with other
fissile materials (except $^{233}$U) was not studied before. Therefore,
the main objective of the present paper is to discuss the simulation of the
\gls{SD-TMSR} operation for a lifetime-long period of time (60 years) with
different initial fissile materials and without any external feed of $^{233}$U
to achieve the thorium fuel cycle transition. We investigated five different
initial fissile materials: \gls{LEU}, Pu mixed with \gls{LEU}, Pu reactor-grade, \gls{TRU} from LWR SNF and $^{233}$U \cite{de2000scenarios}. Moreover, two different feed mechanisms were selected:

\begin{itemize}
	\item Thorium feed mechanism: continuous feed flow of thorium from Th stockpile and $^{233}$U from \texttt{Pa-decay tank}\footnote{An imaginary tank used to store protactinium extracted from the core.}, where the removal rate of $^{233}$Pa = feed rate of $^{233}$U. \cite{betzler2016modeling}.
	\item Non-thorium feed mechanism: continuous injection of Heavy Metal (HM) (excluding Th) and simultaneously feed of all or fraction of $^{233}$U from \texttt{Pa-decay tank}.
\end{itemize}
